### 2024-06-30 multiple-regression.qmd
20240630 - formatting

kable(regression1,
      col.names = c("y","x1"),
      booktabs = TRUE)
```

Using the data, the best fitting regression model is: $y = \text{`{r} regression1_intercept`} + \text{`{r} regression1_slope`} \cdot x_1$.
In this example, the $R^2$ is $\text{`{r} regression1_rsquare`}$.
The equation is not a perfect prediction, but with a single [predictor variable](#sec-correlationalStudy), it captures the majority of the variance in the outcome.

@@

kable(regression2,
      col.names = c("y","x1","x2"),
      booktabs = TRUE)
```

With the second [predictor variable](#sec-correlationalStudy), the best fitting regression model is: $y = \text{`{r} regression2_intercept`} + \text{`{r} regression2_slope1`} \cdot x_1 + \text{`{r} regression2_slope2`} \cdot x_2$.
In this example, the $R^2$ is $\text{`{r} regression2_rsquare`}$.
The equation with the second [predictor variable](#sec-correlationalStudy) provides a perfect prediction of the outcome.

@@

kable(regression3,
      col.names = c("y","x1","x2"),
      booktabs = TRUE)
```

>>>>

kable(
  regression1,
  col.names = c("y","x1"),
  booktabs = TRUE)
```

Using the data, the best fitting regression model is: $y =$ `{r} regression1_intercept` $+$ `{r} regression1_slope` $\cdot x_1$.
In this example, the $R^2$ is `{r} regression1_rsquare`.
The equation is not a perfect prediction, but with a single [predictor variable](#sec-correlationalStudy), it captures the majority of the variance in the outcome.

@@

kable(
  regression2,
  col.names = c("y","x1","x2"),
  booktabs = TRUE)
```

With the second [predictor variable](#sec-correlationalStudy), the best fitting regression model is: $y =$ `{r} regression2_intercept` + `{r} regression2_slope1` $\cdot x_1 +$ `{r} regression2_slope2` $\cdot x_2$.
In this example, the $R^2$ is `{r} regression2_rsquare`.
The equation with the second [predictor variable](#sec-correlationalStudy) provides a perfect prediction of the outcome.

@@

kable(
  regression3,
  col.names = c("y","x1","x2"),
  booktabs = TRUE)
```
